---
title: "P8105 Homework 5"
name: "Jessie Wong"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
library(rvest)
library(tidyr)
```

## Problem 1 

The `data` zip file that we are using in this problem is from a longitudinal study that has a control arm and an experimental arm. 

Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time:

- Started with a dataframe containing all file names; the `list.files` function will help 
- Iterate over file names and read in data for each subject using  purrr::map and saving the result as a new variable in the dataframe
```{r}
data_df = tibble(subject_ID = list.files(path = "./data", pattern = "*.csv", full.names = T)) %>%
  mutate(study1 = map(subject_ID, read_csv)) %>%
  unnest()
```

- Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary
```{r}
study_df = data_df %>%
  gather(key = week, value = observation, week_1:week_8) %>%
  separate(week, into = c("remove_1", "week"), sep = "_") %>%
  separate(subject_ID, into = c("arm", "subject_id"), sep = "_") %>%
  separate(arm, into = c("remove_2", "arm"), sep = 7) %>%
  separate(subject_id, into = c("subject_id", "remove_3"), sep = 2) %>%
  select(-starts_with("remove")) %>%
  arrange(arm, subject_id, week)

study_df$arm[study_df$arm == "con"] = "control"
study_df$arm[study_df$arm == "exp"] = "experimental"
```

Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups
```{r}
study_df %>% 
  group_by(week, arm) %>% 
  ggplot(aes(x = week, y = observation, group = subject_id, color = subject_id)) +
  geom_path() + 
  facet_grid(~arm) +
  labs(title = "Observation Across Study Arm Subjects During Week 1-8") + 
  viridis::scale_color_viridis(
    name = "subject", 
    discrete = TRUE)
```

Based on the spaghetti plot above, we can see a difference in observation values from week 1 to week 8 among the control and experimental subjects. In the control arm, while there are variation across the weeks, the subjects' observation values remained relatively in the same range from week 1 and 8. However, for the experimental arm, we can see an overall increase in observation values from week 1 to week 9 among all of the subjects. 

## Problem 2

The Washington Post has gathered data on homicides in 50 large U.S. cities and made the data available through a GitHub repository. 

Describe the raw data. 
```{r}
# Read the raw data from the Github repository and clean data
homicides = read_csv("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv") 
```
The raw data contains `r nrow(homicides)` cases of homicides across the 50 states. The data reports information about the victims including their age, name (first and last), gender. In addition information about where and when the homicides occurred is also provided, including the city, state, latitude, and longtitude. Finally in the last column there is information about whether the case was solved (closed with arrest) or unsolved (closed without an arrest).

Create a city_state variable (e.g. “Baltimore, MD”) and then summarize within cities to obtain the total number of homicides and the number of unsolved homicides (those for which the disposition is “Closed without arrest” or “Open/No arrest”).
```{r}
# Created a city_state variable
homicides1 = homicides %>%
  mutate(city_state = paste(city, state, sep = ", ")) 

# Summarize total number of homicides
total_hom = homicides1 %>%
  group_by(city_state) %>%
  summarize(total_hom = n()) 

# Summarize total number of unsolved homicides ("Closed without arrest" or "Open/No arrest")  
unsolved_hom = homicides1 %>%
  group_by(city_state) %>%
  filter(disposition %in% c("Closed without arrest", "Open/No arrest")) %>%
  summarize(unsolved_hom = n())
  
```

For the city of Baltimore, MD, use the prop.test function to estimate the proportion of homicides that are unsolved; save the output of prop.test as an R object, apply the broom::tidy to this object and pull the estimated proportion and confidence intervals from the resulting tidy dataframe.
```{r}
# Only using data for city_state "Baltimore, MD"
balt_hom = homicides1 %>%
  filter(city_state == "Baltimore, MD") 

# Identify number of unsolved homicides in Baltimore, MD
balt_hom1 = balt_hom %>%
  group_by(city_state) %>%
  filter(disposition %in% c("Closed without arrest", "Open/No arrest")) %>%
  summarize(unsolved_hom = n()) 
# Unsolved homicides = 1825

# Identify total homicides in Baltimore, MD
balt_hom2 = balt_hom %>%
  filter(city_state == "Baltimore, MD") %>%
  group_by(city_state) %>%
  summarize(total_hom = n()) 
# Total homicides = 2827

# Used prop.test to obtain proportion of homicides that are unsolved 
unsolved_prop = prop.test(1825, 2827, correct = T)

# Applied broom::tidy to obtain estimated proportion and confidence intervals  
unsolved = broom::tidy(unsolved_prop) %>%
    select(estimate, conf.low, conf.high)
```
In Baltimore, MD, there were a total of `r balt_hom1$unsolved_hom` unsolved homicides out of a total of `r balt_hom2$total_hom` homicides in the city. After using `prop.test`, we identified that the estimated proportion of unsolved homicides is `r unsolved_prop$estimate`, with a lower confidence internval of `r unsolved_prop$conf.low` and an upper confidence interval of `r unsolved_prop$conf.high`.

Now run prop.test for each of the cities in your dataset, and extract both the proportion of unsolved homicides and the confidence interval for each. Do this within a “tidy” pipeline, making use of purrr::map,  purrr::map2, list columns and unnest as necessary to create a tidy dataframe with estimated proportions and CIs for each city.
```{r}
hom_info = 
  merge(unsolved_hom, total_hom, by = "city_state")

cities_proportions = function(city_homicides) {
  unsolved_prop = prop.test(city_homicides$unsolved_hom, city_homicides$total_hom, correct = T)
  
  broom::tidy(unsolved_prop) %>%
    select(estimate, conf.low, conf.high)
}

prop_nest = nest(hom_info, unsolved_hom, total_hom) 

prop_unnest = prop_nest %>%
  mutate(unsolved_c = map(.x = data, cities_proportions)) %>%
  unnest()
```

Create a plot that shows the estimates and CIs for each city – check out geom_errorbar for a way to add error bars based on the upper and lower limits. Organize cities according to the proportion of unsolved homicides.
```{r}
prop_unnest %>%
  mutate(city_state = fct_reorder(city_state, estimate)) %>%
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(min = conf.low, max = conf.high)) +
  labs(title = "Proportion of Unsolved Homicides in the US by Cities",
       x = "City and State",
       y = "Unsolved Homicide Proportion") + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  viridis::scale_color_viridis(
    name = "Day", 
    discrete = TRUE)
```

From the `Proportion of Unsolved Homicides in the US by Cities` plot above, we can see that the city with the lowest proportion of unsolved homicides is Richmond, VA and the city with the highest proportion is Chicago, Il. In addition to having the highest proportion, it has the smallest confidence interval length that does not overlap with any of the other cities.  

